quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-03-21 paper-quollr.Rmd
With new updates to the package
Changed the application to new one

@@

@@

## To initialize number of bins along the x-axis
bin1_vec_prism <- 2:25

@@

>>>>

### Interactivity

@@

# Example

@@

## To initialize number of bins along the x-axis
bin1_vec_prism <- 4:25

@@

<!--https://arxiv.org/abs/2409.09227-->

The data used in our study is from APOGEE Data Release 17 (DR17), which encompasses 19 chemical abundances
and stellar parameters for 370,060 stars. This data was obtained through automated analysis of spectra using APOGEE
Stellar Parameter and Chemical Abundances Pipeline (ASPCAP) software (Garc´ıa P´erez et al. 2016). We removed
poor quality stars by ASPCAPFLAG and STARFLAG bitmasks to mitigate potential quality warnings and also
removed outliers and applied standard scale, resulting in a final dataset comprising 133,891 stars.
We focused on chemical abundances, which refer to the relative abundance of different chemical elements in the
atmosphere of stars. To quantify the relative amounts of individual elements, it uses the abundance ratio as the
logarithm of the ratio of two metallic elements in a star relative to their ratio in the sun. For instance, if a star has a
[C/FE] value of -0.08, it means its carbon abundance is 83% that of the Sun. We are using 19 dimensions related to
chemical abundances, including the metallicity [FE/H] and other 18 element abundances.

Compare PCA, tSNE, UMAP, VAE, Autoencoders
